Untwisting the Tetrahelix (v0.4)

### 2017-02-12 doc/TetrahelixUntwist.tex
formula for distance and some arguments about isomophism

@@

  Note: This is a new, simpler proof attempt.
  \begin{theorem}
    Suppose that all edge vertices are on one of three helices of the same positive pitch and the same radius about the $z$ axis differing by $120\degree$ about $z$.
    However, we do not assume that the three helices are equidistant.
    Without loss of generality, consider $A$ and $B$ to be to be on the same axis, $C$ to be on a second axis, and $D$ to be on the final.
    Without loss of generality assume: $A.z \leq C.z \leq D.z \leq B.z$.
    Then the minimum maximum difference between any two nodes is acheived when
    $ \overline{\rm AD} =  \overline{\rm BC} $ and $ \overline{\rm AC} =  \overline{\rm CD}, \overline{\rm DB} $.
  \end{theorem}

  \begin{proof}
\begin{align*}
  O  &= C.z - A.z \\
  G &= D.z - C.z \\
  P &=  B.z - D.z
\end{align*}
First we show any configuration in which $O \neq P$ implies a solution at least as good in terms of minimax difference in which $O = P$.
Let 
\begin{align*}
  \frac{O' + P'}{2} &= \frac{1}{2} + \delta
\end{align*}
Then any configuration $O' - \delta/2, P' - \delta/2$ has a minimax at least as good as $O',P'$, because, if $\delta > 0$, then
$\overline{\rm A'C'}$ is the longest segment of the four $\overline{\rm A'C'}, \overline{\rm A'D'}, \overline{\rm B'C'} =  \overline{\rm B'D'} $.
$\overline{\rm B'D'}$ is the shortest of this set.
\begin{align*}
  \overline{\rm A'D'} &> \overline{\rm B'C'}  \\
   \overline{\rm B'D'} &< \overline{\rm A'C'}  \\  
   \overline{\rm AB} &=   \overline{\rm A'B'}   \\
   \overline{\rm CD} &=   \overline{\rm C'D'}   \\
  \\
   \overline{\rm AC} &=   \overline{\rm BD}   \\
   \overline{\rm AD} &=   \overline{\rm BC}   \\
  \\  
   \overline{\rm AC} &<  \overline{\rm A'C'} \\
   \overline{\rm AD} &< \overline{\rm A'D'}   \\
   \overline{\rm BC} &>  \overline{\rm B'C'} \\
   \overline{\rm BD} &> \overline{\rm B'D'}   \\
\end{align*}
So the maximum $\overline{\rm AD}$ is at most the old maximum. The minimum $\overline{\rm AC}$ is at least the old minimum of our set of four.
If the maximum or minimum of a subset is not worsened, the maximum or minimum of the total set cannot be worsened. Therefore $O' - \delta/2, P' - \delta/2$
is no worse than $O', P'$. So any mimimax solution is no better than one in which $(O + P)/2 = 1/2$, or $O = P$.

Suppose $\overline{\rm C'D'}$ is the shortest edge. Increasing $G$ thereby improves our mimimum, up until the next shortest edge length, $\overline{\rm AC}$.
This may increase $\overline{\rm BC}$ and $\overline{\rm AD}$, but more slowly than $\overline{\rm C'D'}$ is being increased, until  $\overline{\rm C'D'} =
\overline{\rm AC}$.

@@

\begin{theorem}
  Suppose that all edge vertices are on helices about the same axis and that $R,B,Y$ and are $120\degree$ from each other from that axis.
  Then a minimax positioning occurs when at least 3 non-rail edge classes are the longest length and equivalent.
 \end{theorem}
\begin{proof}
Note: It is not perfectly clear this proof is valid for extreme radii which are either very short or very large.

   Suppose that all edge vertices are on helices about the same axis and that $R,B,Y$ and are $120\degree$ from each other from that axis.

  If there is a unique longest distance, it touches two rails. Moving those rails closer together infinitesimally decreases the longest length and
  therefore the minimax.

  Suppose there are exactly two longest edges of equal length. By the pigeonhole principle, these edges must share one rail and touch the other two.
  If moving the shared rail in one direction decreases both edge lengths, doing so infinitesimally decreases the minimax.

  Therefore there must be at least three longest edges of equal length, each of which touches two rails.
  \end{proof}

\begin{theorem}
  Any minimax-optimal tetrahelix at most precisely three classes of edge lengths.
\end{theorem}

\begin{proof}
  Every vertex is connected to each rail by two edges. These two edges cannot be of the same length, unless all six edge classes are the same
  length. If all six are the same length, $Y_0$ and $B_0$ lie on the same $z$ value, but then $green_o$ is much longer than $purple_e = purple_o = orange_e = organge_o$,
  making it a unique longest length, a contradiciton. Therefore the odd and even lengths in each color class are different. Therfore there is a second,
  shorter length, which occurs once in each color class. Taken with the rail edge length of $1$, this makes precisely three classes of equivalent
  edge lengths for any minimax-optimal helix.
\end{proof}

@@

Understand why I can't control color completely!

>>>>

 Any minimax length optimal tetrahelix must have the same pitch on each helix, the length of one set of members grows unboundedly with
 each revolution. So in seeking a minimax optimal tetrahelix we only consider those with the same torsion.

 We show that in fact the nodes must be distributed in even thirds along the $z$-axis.

@@

 First prove that any structure isomorphic to the BC-Helix of unbounded extent in which each rail lies on a helix has certain
 properties if it it member length minimax optimal.

 The pitches must be equal, or some member grows without bound.

 If the axes are not parallel, some member grows without bound.

 We can therefore think in terms of O,G, P displacement.

 We need to prove that the three axes are coincident.

 Suppose there is one helix that is not conicident with the other two.  So long as $\rho \neq 0$, there is some value of $\kappa$
 makes the lenth to any node longer and shorter. Then the distance between nodes depends on $\kappa$, unless $\rho = 0$ or $\rho = \pi$.
 One of these makes the longest distance longer and the shortest distance shorter, so a superior solution occurs when the a
 axes conincide.  This is actually correct but poorly written.

 Now now that we have coincident axes, the same pitch, we can go on to the hard proof about where they occur.

  Note: This is a new, simpler proof attempt.
  \begin{theorem}
    Suppose that all edge vertices are on one of three helices of the same positive pitch and the same radius with the
    same shared axes about the $z$ axis differing by $120\degree$ about $z$.
    However, we do not assume that the three helices are equidistant.
    Without loss of generality, consider $A$ and $B$ to be to be on the same axis, $C$ to be on a second axis, and $D$ to be on the final.
    Without loss of generality assume: $A.z \leq C.z \leq D.z \leq B.z$.
    Then the minimum maximum difference between any two nodes is acheived when
    $ \overline{\rm AD} =  \overline{\rm BC} $ and $ \overline{\rm AC} =  \overline{\rm CD}, \overline{\rm DB} $.
  \end{theorem}
Note: Change this to PQR. Also, may be better to use $\alpha$ instead of $\rho$ in this proof.
  \begin{proof}
\begin{align*}
  O  &= C.z - A.z \\
  G &= D.z - C.z \\
  P &=  B.z - D.z
\end{align*}

Using the cartesian distance formula:
\begin{align*}
  \overline{\rm CD}  &= \sqrt{G^2 + (r\sin{0 \rho} -  r\sin{G \rho})^2 + (r\cos{0 \rho} - r\cos{G \rho})^2} \\
    \overline{\rm CD}  &= \sqrt{G^2 + (0 -  r\sin{G \rho})^2 + (r - r\cos{G \rho})^2} \\
    \overline{\rm CD}  &= \sqrt{G^2 + r^2(\sin{G \rho})^2 + r^2(1 - \cos{G \rho})^2} \\
    \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + \sin^2{G \rho}  - \cos^2{G \rho})} \\    
\end{align*}

Note: According to Wolfram Alpha, $\sin^2{G \rho}  - \cos^2{G \rho} = -\cos{2 G \rho}$

So, for all O,G,P,
\begin{align*}
  \overline{\rm AB}  &= 1 \\        
  \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + \sin^2{G \rho}  - \cos^2{G \rho})} \\
  \overline{\rm AC}  &= \sqrt{O^2 + r^2(1 + \sin^2{O \rho}  - \cos^2{O \rho})} \\
  \overline{\rm BD}  &= \sqrt{P^2 + r^2(1 + \sin^2{P \rho}  - \cos^2{P \rho})} \\
  \overline{\rm AD}  &= \sqrt{(O+G)^2 + r^2(1 + \sin^2{(O +G) \rho}  - \cos^2{(O+G) \rho})} \\
  \overline{\rm BC}  &= \sqrt{(P+G)^2 + r^2(1 + \sin^2{(P +G) \rho}  - \cos^2{(P+G) \rho})} \\      
\end{align*}

We show that the maximum difference between these variables for a given $r$ is minimized when $O=G=P=1/3$.
First we show any configuration in which $O \neq P$ implies a solution at least as good in terms of minimax difference in which $O = P$.
Let 
\begin{align*}
  \frac{O' + P'}{2} &= \frac{1}{2} + \delta
\end{align*}
Then any configuration $O' - \delta/2, P' - \delta/2$ has a minimax at least as good as $O',P'$, because, if $\delta > 0$, then
$\overline{\rm A'C'}$ is the longest segment of the four $\overline{\rm A'C'}, \overline{\rm A'D'}, \overline{\rm B'C'} =  \overline{\rm B'D'} $.
$\overline{\rm B'D'}$ is the shortest of this set.
\begin{align*}
  \overline{\rm A'D'} &> \overline{\rm B'C'}  \\
   \overline{\rm B'D'} &< \overline{\rm A'C'}  \\  
   \overline{\rm AB} &=   \overline{\rm A'B'}   \\
   \overline{\rm CD} &=   \overline{\rm C'D'}   \\
  \\
    \overline{\rm AC}&=   \overline{\rm BD}   \\
   \overline{\rm AD} &=   \overline{\rm BC}   \\
  \\  
   \overline{\rm AC} &<  \overline{\rm A'C'} \\
   \overline{\rm AD} &< \overline{\rm A'D'}   \\
   \overline{\rm BC} &>  \overline{\rm B'C'} \\
   \overline{\rm BD} &> \overline{\rm B'D'}   \\
\end{align*}
So the maximum $\overline{\rm AD}$ is at most the old maximum. The minimum $\overline{\rm AC}$ is at least the old minimum of our set of four.
If the maximum or minimum of a subset is not worsened, the maximum or minimum of the total set cannot be worsened. Therefore $O' - \delta/2, P' - \delta/2$
is no worse than $O', P'$. So any mimimax solution is no better than one in which $(O + P)/2 = 1/2$, or $O = P$.

Suppose $\overline{\rm C'D'}$ is the shortest edge. Increasing $G$ thereby improves our mimimum, up until the next shortest edge length, $\overline{\rm AC}$.
This may increase $\overline{\rm BC}$ and $\overline{\rm AD}$, but more slowly (???) than $\overline{\rm C'D'}$ is being increased, until  $\overline{\rm C'D'} =
\overline{\rm AC}$.
Note: This is sketchy, can we show that the derivative of our formula for CD  with respect to $G$ is really higher than $AD$? These derivatives will depend on $\rho$ slightly, which is exactly right!

@@

@@

Remove the weirdly colored diagram.

Add to the rail angle diagram.
